A Particle Swarm Optimisation-Based Indirect Approach to Web Service Composition

### 2015-10-07 paper.tex
Writing literature review.

One important group of techniques to Web service composition focuses on creating a correct composition workflow, where atomic services are connected in a way that can be executed at runtime (e.g. planning approaches) \cite{}. Another group focuses on optimising the quality of compositions, assuming that an abstract workflow is already known for the composition and then employing optimisation techniques to bind the best possible set of concrete services to this existing structure \cite{}. A third group of approaches attempts to address both of these concerns simultaneously, creating a correct workflow at the same time that it optimises the quality of the services included in the composition \cite{da2015graphevol}. However, simultaneously accomplishing these two tasks increases the complexity of these approaches, since the optimisation must also respect a number of interrelated constraints \cite{venkatraman2005generic}.

@@

>>>>

One important group of techniques to Web service composition focuses on creating a correct composition workflow, where atomic services are connected in a way that can be executed at runtime \cite{}. Another group focuses on optimising the quality of compositions, assuming that an abstract workflow is already known for the composition and then employing optimisation techniques to bind the best possible set of concrete services to this existing structure \cite{}. A third group of approaches attempts to address both of these concerns simultaneously, creating a correct workflow at the same time that it optimises the quality of the services included in the composition \cite{da2015graphevol}. However, simultaneously accomplishing these two tasks increases the complexity of these approaches, since the optimisation must also respect a number of interrelated constraints \cite{venkatraman2005generic}.

@@

A wide variety of Evolutionary Computing (EC) approaches has been applied to the problem of Web service composition, as evidenced by literature surveys of the field \cite{wang2012survey,pejman2012web}. One of the earliest works in this area \cite{canfora2005approach} applies genetic algorithms to optimise the overall Quality of Service (QoS) of a composition. The composition process in this work is \textit{semi-automated}, meaning that a workflow of abstract services has already been provided. In semi-automated compositions, the objective is to select a set of concrete services that fulfil the required functionality of their abstract counterparts, ensuring that the selected set results in a composition with the best possible quality. Even this approach takes QoS into account, it is not capable of performing \textit{fully automated} composition, which is when the composition workflow is automatically deduced at the same time that the services to include in the composition are identified.

* A semi-automated PSO approach to Web service composition (\cite{zhao2012improved})

Another approach \cite{rodriguez2010composition} employs Genetic Programming (GP) to perform fully automated Web service composition, representing solutions as a trees with candidate services as the leaf nodes and composition constructs as the inner nodes. A context-free grammar is used to generate new individuals at the beginning of the evolutionary process, as well as ensuring structural correctness during the crossover and mutation operations. Despite its favourable experimental results, this approach has the shortcoming of neglecting the Quality of Service of compositions, instead optimising candidates according to workflow topology measures such as the length of the longest path in the composition and the number of atomic services included.

* QoS-aware Web GP approach (use Yang's \cite{yu2013adaptive})

* GraphEvol approach \cite{da2015graphevol}
